---
title: "Precourse Assignment"
author: "Dionna Attinson"
date: "1/20/2020"
output: html_document
---
```{r}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(fBasics)
library(data.table)
library(ggplot2)
library(plotly)
library(patchwork)
library(viridis)
options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)
scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d
theme_set(theme_bw() + theme(legend.position = "right"))
theme_set(theme_minimal() + theme(legend.position = "right"))
knitr::opts_chunk$set(
  collapse = TRUE,
  fig.width = 6,
  fig.asp = .6,
	echo = TRUE,
	warning = FALSE,
	fig.width = 8, 
  fig.height = 6,
  out.width = "90%")
```

#### First, we will read in the dataset and name it `Data`
```{r}
Data = read_csv("./dataR2.csv")
```
#### Next, we will create a summary output of the dataset. 
```{r}
basicStats(Data)[c("Mean", "Stdev", "Median", "Minimum", "Maximum"),] %>% 
  knitr::kable(digits = 1)
```

#### Now, we will recode BMI into the WHO-defined categories below 
* +Severely underweight - BMI less than 16.5kg/m^2 
* +Underweight - BMI under 18.5 kg/m^2 
* +Normal weight - BMI greater than or equal to 18.5 to 24.9 kg/m^2 
* +Overweight – BMI greater than or equal to 25 to 29.9 kg/m^2 
* +Obesity class I – BMI 30 to 34.9 kg/m^2 
* +Obesity class II – BMI 35 to 39.9 kg/m^2 
* +Obesity class III – BMI greater than or equal to 40 kg/m^2

```{r}
Data = 
  Data %>% 
  mutate(
    BMI_Category = BMI,
    BMI_Category = as.numeric(BMI_Category),
    Classification = as.character(Classification))
```

```{r}
Data = 
 Data %>% 
 mutate(BMI_Category = 
          case_when(BMI_Category >= 40 ~ 'Obesity Class III',
                    BMI_Category >= 35  & BMI_Category <= 39.9 ~ 'Obesity Class II',
                    BMI_Category >= 30  & BMI_Category <= 34.9 ~ 'Obesity Class I',
                    BMI_Category >= 25  & BMI_Category <= 29.9 ~ 'Overweight',
                    BMI_Category >= 18.5  & BMI_Category <= 24.9  ~ 'Normal Weight',
                    BMI_Category >= 16.5 & BMI_Category <= 18.4 ~ 'Underweight',
                    BMI_Category <= 16.4 ~ "Severely Underweight"))
```
### Now we will Create a bar chart showing the proportion of breast cancer cases and controls within each BMI category
```{r}
PlotData = 
Data %>% 
    mutate(Classification = 
             recode(Classification,
                    "1" = "Controls",
                    "2" = "Cases"))
```

```{r}
plot2 = 
 PlotData %>% 
 ggplot(aes(x=BMI_Category, fill=Classification)) +
 geom_bar() 

ggplotly(plot2)
```

### Now we will create a logistic and linear regression model 
* Construct a logistic regression model using breast cancer classification as the outcome and glucose, HOMA, leptin, BMI (continuous) and age as the independent variables. 
* Fill in the beta estimate and 95% confidence interval associated with a 1-unit change in HOMA5.
* Construct a linear regression model using insulin as the outcome and BMI (continuous), age, and glucose as the independent variables. 
* Fill in the beta estimate and 95% confidence interval associated with a 1-unit change in age.
```{r}
Data_Regression = 
  Data %>% 
  mutate(
    Classification = recode(Classification, 
              "1" = "0", 
              "1" = "0",
              "2" = "1",
              "2" = "1"),
    Classification = as.numeric(Classification))
```

```{r}
model1 = 
  Data_Regression %>% 
  glm(Classification ~ Glucose + HOMA + Leptin + BMI + Age, data = ., family =  binomial())
 
model1 %>% 
  broom::tidy() %>% 
  mutate(OR = exp(estimate),
         High_CI = exp(estimate + 1.96*std.error),
         Low_CI = exp(estimate - 1.96*std.error)) %>% 
  select(term, log_OR = estimate, OR, p.value, Low_CI, High_CI) %>% 
  knitr::kable(digits = 3)
```

```{r}
model2 = 
  Data_Regression %>% 
  lm(Insulin ~ BMI + Age + Glucose, data = .,)

model2 %>% 
  broom::tidy() %>% 
  mutate(OR = exp(estimate),
         High_CI = exp(estimate + 1.96*std.error),
         Low_CI = exp(estimate - 1.96*std.error)) %>% 
  select(term, log_OR = estimate, OR, p.value, Low_CI, High_CI) %>% 
  knitr::kable(digits = 3)
```

