---
title: "Machine Learning Precourse Assignment"
author: "Dionna Attinson, dna2118"
date: "1/20/2020"
output:
  word_document: default
  html_document: default
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
```

#### Step 1: First, we will read in the dataset and name it `Data`

```{r}
Data = read_csv("./dataR2.csv")
```

#### Step 2: Next, we will create a summary output of the dataset

```{r}
Data %>% 
  select(-Classification) %>% 
  summary(Data) %>% 
  knitr::kable(digits = 1)
```

#### Step 3: Now, we will recode BMI into the WHO-defined categories below 
* +Severely underweight - BMI less than 16.5kg/m^2 
* +Underweight - BMI under 18.5 kg/m^2 
* +Normal weight - BMI greater than or equal to 18.5 to 24.9 kg/m^2 
* +Overweight – BMI greater than or equal to 25 to 29.9 kg/m^2 
* +Obesity class I – BMI 30 to 34.9 kg/m^2 
* +Obesity class II – BMI 35 to 39.9 kg/m^2 
* +Obesity class III – BMI greater than or equal to 40 kg/m^2

```{r}
Data = 
  Data %>% 
  mutate(
    BMI_Category = BMI,
    BMI_Category = as.numeric(BMI_Category),
    Classification = as.character(Classification))
```

```{r}
Data = 
 Data %>% 
 mutate(BMI_Category = 
          case_when(BMI_Category >= 40 ~ 'Obesity Class III',
                    BMI_Category >= 35  & BMI_Category <= 39.9 ~ 'Obesity Class II',
                    BMI_Category >= 30  & BMI_Category <= 34.9 ~ 'Obesity Class I',
                    BMI_Category >= 25  & BMI_Category <= 29.9 ~ 'Overweight',
                    BMI_Category >= 18.5  & BMI_Category <= 24.9  ~ 'Normal Weight',
                    BMI_Category >= 16.5 & BMI_Category <= 18.4 ~ 'Underweight',
                    BMI_Category <= 16.4 ~ "Severely Underweight"))
```

#### Step 4: Now we will create a bar chart showing the proportion of breast cancer cases and controls within each BMI category

```{r}
PlotData = 
Data %>% 
    mutate(Classification = 
             recode(Classification,
                    "1" = "Controls",
                    "2" = "Cases"))
```

```{r}
PlotData %>% 
ggplot(aes(x=BMI_Category, fill=Classification)) +
geom_bar() 
```

#### Step 5: Now we will create a logistic and linear regression model using the variables provided
* Construct a logistic regression model using breast cancer classification as the outcome and glucose, HOMA, leptin, BMI (continuous) and age as the independent variables. 
* Fill in the beta estimate and 95% confidence interval associated with a 1-unit change in HOMA5.
* Construct a linear regression model using insulin as the outcome and BMI (continuous), age, and glucose as the independent variables. 
* Fill in the beta estimate and 95% confidence interval associated with a 1-unit change in age.

```{r}
Data_Regression = 
  Data %>% 
  mutate(
    Classification = recode(Classification, 
              "1" = "0", 
              "1" = "0",
              "2" = "1",
              "2" = "1"),
    Classification = as.numeric(Classification))
```

```{r}
model1 = 
  Data_Regression %>% 
  lm(Classification ~ Glucose + HOMA + Leptin + BMI + Age, data = ., family =  binomial())
 
model1 %>% 
  broom::tidy() %>% 
  filter(term == "HOMA") %>% 
  mutate(OR = exp(estimate),
         High_CI = exp(estimate + 1.96*std.error),
         Low_CI = exp(estimate - 1.96*std.error)) %>% 
  select(term, log_OR = estimate, OR, p.value, Low_CI, High_CI) %>% 
  knitr::kable(digits = 3) 
```

#### In the logistic regression above, we see that at a 5% level of significance, cases have 1.315 times the odds for HOMA in comparison to the control group. We are 95% confident that the true odds lies between 0.973 and 1.038.

```{r}
model2 = 
  Data_Regression %>% 
  lm(Insulin ~ BMI + Age + Glucose, data = .,)

model2 %>% 
  broom::tidy() %>% 
  filter(term == "Age") %>% 
  mutate(High_CI = exp(estimate + 1.96*std.error),
         Low_CI = exp(estimate - 1.96*std.error)) %>% 
  select(term, estimate, p.value, Low_CI, High_CI) %>% 
  knitr::kable(digits = 3)
```

#### In the linear regression above, we see that at a 5% level of signficance, for every one unit increase in age, insulin decreases by 0.054. 
